Online analysis supplement

### 2021-11-03 index.Rmd
Reparameterise gbd time models

```{r settings}
# Packages
library(readxl)
library(brms)
library(ragg)
library(scales)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(parameters)
library(countrycode)
library(multidplyr)
library(lme4)
library(emmeans)
library(plotly)
library(knitr)
library(patchwork)
library(bayestestR)
library(lubridate)
library(haven)
library(janitor)
library(broom)
library(kableExtra)
library(ggbeeswarm)
library(ggstance)
library(sysfonts)
library(tidyverse)

@@

# Plotting theme
Font <- "Titillium Web"
if (!(Font %in% font_families())) font_add_google(Font, Font)
theme_set(
  theme_linedraw(
    base_size = 12, 
    base_family = Font
  ) +
    theme(
      panel.grid = element_blank(),
      strip.text = element_text(margin = margin(4,4,4,4, "pt"))
    )
)

# MCMC settings
options(brms.backend = "cmdstanr")
# Run this to delete fitted models and refit
# unlink(list.files(pattern = "brm-.*\\.rds"))

# parallel computations
MAX_CORES <- as.numeric(Sys.getenv("MAX_CORES"))
if (is.na(MAX_CORES)) MAX_CORES <- parallel::detectCores(logical = FALSE)
cluster <- new_cluster(MAX_CORES)
cluster_library(cluster, c("lme4", "dplyr", "stringr"))

@@

```{r}
# Calculate numbers of missing values for fixed (2004-) and mobile (2007-)
bind_rows(
  select(itu, Internet) %>% 
    naniar::miss_var_summary(),
  filter(itu, Year >= 2004) %>% 
    select(Fixed) %>% 
    naniar::miss_var_summary(),
  filter(itu, Year >= 2007) %>% 
    select(Mobile) %>% 
    naniar::miss_var_summary()
) %>% 
  mutate(pct_miss = percent(pct_miss/100)) %>% 
  kbl(caption = "ITU Missingness") %>% 
  kable_styling(full_width = FALSE)
```

@@

```{r}
# Plot predictors from their own table--values are repeated in data that includes outcomes due to age and sex groups for each year and country
p_itu <- itu %>% 
  mutate(Year = make_date(Year)) %>% 
  # Do something about countries with no region if they have outcome data
  drop_na(Region) %>% 
  pivot_longer(c(Fixed, Mobile, Internet), names_to = "Type") %>% 
  mutate(Type = factor(Type, levels = c("Internet", "Fixed", "Mobile"))) %>% 
  ggplot(
    aes(
      x = Year, 
      y = value, 
      group = interaction(Type, Country)
    )
  ) +
  coord_cartesian(ylim = c(0, 1.00)) +
  scale_y_continuous(
    "Internet users (or subscriptions) / population",
    breaks = c(0, .25, .5, .75, 1),
    labels = percent,
    expand = expansion(c(0.02, 0.1))
  ) +
  scale_x_date(
    breaks = breaks_width("5 years"),
    labels = label_date("'%y")
  ) +
  geom_line(size = .25, col = "dodgerblue4") +
  facet_grid(Type~Region) +
  theme(legend.position = "none")
agg_png("output/Fig-ITU.png", height = 1200, width = 3200, res = 300)
p_itu
dev.off()
agg_png("output/Fig-ITU-internet.png", height = 1200, width = 3200, res = 300)
p_itu %+% 
  (filter(p_itu$data, Type == "Internet") %>% 
     mutate(Region = str_replace(Region, "\n", " "))) + 
  scale_y_continuous(
    "Internet users / population",
    breaks = c(0, .25, .5, .75, 1),
    labels = percent,
    expand = expansion(c(0.02, 0.1))
  ) +
  facet_wrap("Region", nrow = 2)
dev.off()
```

@@

p_gbd

ggsave(
  "output/Fig-GBD.png", 
  device = agg_png,
  height = 2400, width = 3600, res = 300, units = "px"
)
```

@@

```{r fit-gbd-time-brms}
fit_empty <- brm(
  val ~ Time * Sex + 
    (1 + Time * Sex | Country) +
    (1 + Time * Sex | Region) +
    (1 + Time * Sex | Age),
  data = filter(d, Cause == "Depression"),
  file = "output/brm-gbd-time-empty",
  chains = 0,
  threads = 3,
)

# cluster_copy(cluster, "fit_empty")
fits_brm <- d %>% 
  group_by(Cause) %>% 
  summarise(
    fit = list(
      update(
        fit_empty,
        newdata = cur_data_all(),
        chains = 4,
        cores = 4,
        iter = 1600,
        warmup = 800,
        refresh = 10,
        threads = 3,
        file = str_glue("output/brm-gbd-time-{cur_group()}")
      )
    )
  ) %>%
  ungroup()
```

>>>>

```{r settings}
# Packages
library(readxl)
library(brms)
library(ragg)
library(scales)
library(ggh4x)
library(tidybayes)
library(naniar)
library(ggdist)
library(parameters)
library(countrycode)
library(multidplyr)
library(lme4)
library(emmeans)
library(plotly)
library(knitr)
library(patchwork)
library(bayestestR)
library(lubridate)
library(haven)
library(janitor)
library(broom)
library(kableExtra)
library(ggbeeswarm)
library(ggstance)
library(sysfonts)
library(tidyverse)

@@

# Plotting theme
Font <- "Titillium Web"
if (!(Font %in% font_families())) font_add_google(Font, Font)
theme_set(
  theme_linedraw(
    base_size = 12, 
    base_family = Font
  ) +
    theme(
      panel.grid = element_blank(),
      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
    )
)

# MCMC settings
options(brms.backend = "cmdstanr")
# Run this to delete fitted models and refit
# unlink(list.files(pattern = "output/brm-.*\\.rds"))

# parallel computations
MAX_CORES <- parallel::detectCores(logical = TRUE) / 2
cluster <- new_cluster(MAX_CORES)
cluster_library(cluster, c("lme4", "dplyr", "stringr"))

@@

```{r}
# Calculate numbers of missing values for fixed (2004-) and mobile (2007-)
bind_rows(
  select(itu, Internet) %>% 
    miss_var_summary(),
  filter(itu, Year >= 2004) %>% 
    select(Fixed) %>% 
    miss_var_summary(),
  filter(itu, Year >= 2007) %>% 
    select(Mobile) %>% 
    miss_var_summary()
) %>% 
  mutate(pct_miss = percent(pct_miss/100)) %>% 
  kbl(caption = "ITU Missingness") %>% 
  kable_styling(full_width = FALSE)
```

@@

```{r}
# Plot predictors from their own table--values are repeated in data that includes outcomes due to age and sex groups for each year and country
p_itu <- itu %>% 
  mutate(Year = make_date(Year)) %>% 
  # Do something about countries with no region if they have outcome data
  drop_na(Region) %>% 
  pivot_longer(c(Fixed, Mobile, Internet), names_to = "Type") %>% 
  mutate(Type = factor(Type, levels = c("Internet", "Fixed", "Mobile"))) %>% 
  ggplot(
    aes(
      x = Year, 
      y = value, 
      group = interaction(Type, Country)
    )
  ) +
  coord_cartesian(ylim = c(0, 1.00)) +
  scale_y_continuous(
    "Internet users (or subscriptions) / population",
    breaks = c(0, .25, .5, .75, 1),
    labels = percent,
    expand = expansion(c(0.02, 0.1))
  ) +
  scale_x_date(
    breaks = breaks_width("5 years"),
    labels = label_date("'%y")
  ) +
  geom_line(size = .25, col = "dodgerblue4") +
  facet_grid(Type~Region) +
  theme(legend.position = "none")

p_itu
ggsave(
  "output/Fig-ITU.png", 
  device = agg_png,
  height = 2400, width = 3200, res = 300, units = "px"
)

p_itu %+% 
  (filter(p_itu$data, Type == "Internet") %>% 
     mutate(Region = str_replace(Region, "\n", " "))) + 
  scale_y_continuous(
    "Internet users / population",
    breaks = c(0, .25, .5, .75, 1),
    labels = percent,
    expand = expansion(c(0.02, 0.1))
  ) +
  facet_wrap("Region", nrow = 2)
ggsave(
  "output/Fig-ITU-internet.png", 
  device = agg_png,
  height = 1200, width = 3200, res = 300, units = "px"
)
```

@@

p_gbd
ggsave(
  "output/Fig-GBD.png", 
  device = agg_png,
  height = 2400, width = 3600, res = 300, units = "px"
)
```

@@

```{r fit-gbd-time-brms}
fit_empty <- brm(
  val ~ 0 + Sex:Age + Time:Sex:Age + 
    (0 + Sex:Age + Time:Sex:Age | Country) +
    (0 + Sex:Age + Time:Sex:Age | Region),
  data = filter(d_young, Cause == "Depression"),
  file = "output/brm-gbd-time-empty",
  chains = 0,
  threads = 3,
)

fits_brm <- d_young %>% 
  group_by(Cause) %>% 
  summarise(
    fit = list(
      update(
        fit_empty,
        newdata = cur_data_all(),
        chains = 4,
        cores = 4,
        iter = 1600,
        warmup = 800,
        refresh = 10,
        threads = 3,
        file = str_glue("output/brm-gbd-time-{cur_group()}")
      )
    )
  ) %>%
  ungroup()
```
